Shades of Green in the Swedish Forest-Based Bioeconomy Transition

### 2023-09-22 docs/reports/paper/paper1.qmd
add doublespaced lines

csl: https://zotero.org/styles/apa?source=1
bibliography: [../../swinno-shades-green.bib]
link-citations: true
link-bibliography: true
colorlinks: true
number-sections: true
format:
    wordcount-pdf: 
        papersize: A4
execute:
    include: true
    echo: false
    warning: false
---

>>>>

csl: https://zotero.org/styles/apa?source=1
bibliography: [../../swinno-shades-green.bib]
link-citations: true
link-bibliography: true
colorlinks: true
number-sections: true
format:
    wordcount-pdf: 
        papersize: A4
        linestretch: 1.5
execute:
    include: true
    echo: false
    warning: false
---
